\section{Chapter Overview}
This final chapter is where we will conclude the project. We will talk once again about the  aims and objectives of the project and evaluate whether or not they were met in the completion of the web application.
\newline
\newline
We believe we have achieved what we initially set out to create by developing a restaurant Point of Sale and Management System on the other hand we have also failed to meet all objectives as currently the restaurant Point of Sale and Management System is not hosted on the cloud resulting in remote order being impossible. Throughout the documentation we have shown the tools as well as methodologies that were needed in the developing the final product which allows the user to all the functionality that would be expected when using a restaurant Point of Sale and Management System. As listed in the introduction, objectives were defined :

\begin{itemize}
  \item User Authentication
  \item Till GUI
  \item Sales
  \item Receipts/Hardware
  \item Reports
  \item Users
  \item Categories
  \item Products
  
\end{itemize}

\section{Reflection}

As mentioned earlier in the documentation System Evaluation, We are happy that we have achieved all that we initially set out to do. In conclusion we feel that we have provided an extensive report to the reader with insights into the technologies that were used in the development of our Web application along with the importance the technologies played in the development of the project.

\section{Learning Outcome}
Thought the development of this project both of us have acquired a large amount of knowledge on a variety of technologies and languages that went into the development of this project. Initially Php was foreign to us as it was something that we had never employed before, it was very challenging while also very rewarding learning  new languages such as  Php and Java Script. Java Script was another language which we felt our knowledge was inadequate with and was an extremely helpful to learn these two combined with using many of the plugins that were employed in the development of the project such as TC-PDF which allowed us to create PDF's with outputs of our database tables. The skills obtained in the development of this product such as the importance of working in a development team,we feel will help us immensely as we both move on in life as future software developers.

\section{GitHub}
Link to navigate to the GitHub where our project was developed:
\newline
\url{https://github.com/markgilmore10/Final-Year-project}