\chapter{Technology Review}
\section{Technologies}
\subsection{Adminlte}
For the main look and design of the project we decided to use AdminLTE. AdminLTE is an open source administration dashboard template. It is built on top of bootstrap which made it easy to adapt and shape to match our needs and goals.
\subsection{Ionicons}
Ionicons are bootstrap icons we used for table icons throughout the project. They offer an added sense of professionalism and make the project look aesthetically pleasing.
\subsection{Bootstrap}
Bootstrap is an open-source CSS framework that we used for the buttons and used as part of AdminLTE for tables and forms.
\subsection{Font awesome} 
Font and icon toolkit based on CSS.
\subsection{Bootstrap data tables}
We used the Bootstrap Datatables plugin for all of our tables. This allows for the sorting and searching of tables items without the need for any extra code. 
\subsection{jQuery}
jQuery is a JavaScript library designed to simplify HTML DOM tree traversal and manipulation, as well as event handling, CSS animation, and Ajax. [Quote]
\subsection{jQuery Number}
Used to format numbers
\subsection{Fastclick}
FastClick is a simple, easy-to-use library for eliminating the 300ms delay between a physical tap and the firing of a click event on mobile browsers
\subsection{Sweet alert}
A beautiful, responsive, customizable and accessible (WAI-ARIA) replacement for JavaScript's popup boxes
Input mask
Used to format input (email, numbers, dates)
\subsection{Xampp}
XAMPP is a free and open-source cross-platform web server solution stack package developed by Apache Friends, consisting mainly of the Apache HTTP Server, MariaDB database, and interpreters for scripts written in the PHP and Perl programming languages
\subsection{Visual Studio Code}
Visual Studio Code is a source-code editor developed by Microsoft for Windows, Linux and macOS. It includes support for debugging, embedded Git control and GitHub, syntax highlighting, intelligent code completion, snippets, and code refactoring
\subsection{MySQL}
MySQL is an open-source relational database management system. Its name is a combination of "My", the name of co-founder Michael Widenius's daughter, and "SQL", the abbreviation for Structured Query Language
\subsection{Latex}
LaTeX is a document preparation system. When writing, the writer uses plain text as opposed to the formatted text found in "What You See Is What You Get" word processors like Microsoft Word, LibreOffice Writer and Apple Pages
